Gravitational Lens Recovery with \Glass: Measuring the mass profile and shape of a lens

### 2014-06-13 limits/ms.tex
Updated figures with 'Z' labels and better shaded errors.

\documentclass[galley,usenatbib]{mn2e}
%\documentclass[twocolumn,galley]{mn2e}
%\documentclass[onecolumn,galley,draft]{mn2e}
\usepackage{myaasmacros}
\usepackage{mathrsfs}
\usepackage{amsmath}
\usepackage{graphicx}
%\usepackage{ulem} % Only necessary for striking out TODO items see \sout
\usepackage{color} % Only necessary for hilight

@@

%-------------------------------------------------------------------------------
% Macros for notes.
%-------------------------------------------------------------------------------
\newcommand{\hilight}[1]{{\bf \color{red} #1}}

@@

In the simplest form, a single model for a lens is a tuple $\M = (\vec\kappa,
\vec\beta, \gamma_1, \gamma_2)$. A single model represents a single point in
the solution space polytope. Using the MCMC sampling strategy described in
\cite{2012MNRAS.425.3077L} we uniformly sample this space. Collectively, the
sampled models are referred to as an ensemble $\E = \{\M_i\}$, where we usually
generate $|\E| \sim 1000$ models. One can choose to further process these
models to impose further priors that may be difficult to enforce during the
modeling process. For instance, non-linear constraints, or simply filtering
of models that do not meet some criteria can be excluded, or weighted against.
For our current analysis, we do not exclude any models.

The time to generate the model ensemble is mostly a function of the size of the
parameter space. The MCMC algorithm has a ``warm-up'' phase where it estimates
the size and shape of each dimension in the solution space.  Once this has been
completed, the models are sampled very quickly. In fact, there is little
difference between generating 1,000 or 10,000 models. For our problems, the
typical ``warm-up'' time was about 4s, and the modelling time was 20s using a
parallel shared-memory machine with 40 cores.

@@

\begin{enumerate}
\item one double and one extended double;
\item one quad and one extended quad;
\item two 2-source quads with varying redshift contrast.
\end{enumerate}
The `extended' configurations use multiple point sources at the same redshift
to simulate an extended source that will produces an arc-like image.
\figref{arrival surfaces} shows the lens configurations for the \mockBC\
galaxy. 
The configurations for the other galaxies are similar. Within the
names, the labels Z1, Z2, Z3 refer to the redshift of the sources. We have
chosen Z1=1.72, Z2=0.72, and Z3=0.51 so that the radial distribution of the
images is nearly equal. For all mocks, we do not apply any external shear field.
Only the central image of the Z1 source is used to avoid overconstraining
the models, otherwise all the central images would fall within the central 
pixel and no solution exists that satisfies all locations simultaneously for
one pixel value.

@@

\figref{main results} and \figref{main results pixel-wise} show the results for
our full mock data ensemble. Each subplot corresponds to a different mock
galaxy, as marked. We show the fractional error of the mass distribution for
each of the test configurations with (red) and without (black) stellar mass. In
\figref{main results} we define the error
%
\begin{equation} \label{ferror R}
  f_R = \frac {\sum_i \left|M(i) - \tilde M(i)\right| } {\sum \tilde M(i)}
\end{equation}
%
based on the mass $M(i)$ of each pixel ring $i$ and the mass $\tilde M$ from the mock galaxy. 
In \figref{main results pixel-wise} the error is defined over all the pixels $\vec\theta$:
%
\begin{equation} \label{ferror theta}
f_\theta = \frac {\sum_{\vec\theta} \left|M(\vec\theta) - \tilde M(\vec\theta)\right| } {\sum_{\vec\theta} \tilde M(\vec\theta)}
\end{equation}
%
For both $f_R$ and $f_\theta$, we only consider mass up to one pixel length
passed the outermost image, since there is no longer any lensing information
beyond that point. This means we typically use 8 bins, linearly spaced,
ignoring the outermost 3 bins.  The spacing changes, however, at the border
between the high resolution region in the middle.

>>>>

\documentclass[galley,usenatbib]{mn2e}
%\documentclass[twocolumn,galley]{mn2e}
%\documentclass[onecolumn,galley,draft]{mn2e}
\usepackage{myaasmacros}
\usepackage{mathrsfs}
\usepackage{amsmath}
\usepackage{graphicx}
%\usepackage{ulem} % Only necessary for striking out TODO items see \sout
\usepackage[usenames,dvipsnames]{color} % Only necessary for hilight

@@

%-------------------------------------------------------------------------------
% Macros for notes.
%-------------------------------------------------------------------------------
\newcommand{\hilight}[1]{{\bf \color{OliveGreen} #1}}

@@

In the simplest form, a single model for a lens is a tuple $\M = (\vec\kappa,
\vec\beta, \gamma_1, \gamma_2)$. A single model represents a single point in
the solution space polytope. Using the MCMC sampling strategy described in
\cite{2012MNRAS.425.3077L} we uniformly sample this space. Collectively, the
sampled models are referred to as an ensemble $\E = \{\M_i\}$, where we usually
generate $|\E| \sim 1000$ models. One can choose to further process these
models to impose priors that may be difficult to enforce during the
modeling process. For instance, non-linear constraints, or simply filtering
of models that do not meet some criteria can be excluded, or weighted against.
For the current analysis, we do not exclude any models and treat all models
as equally likely.

The time to generate the model ensemble is mostly a function of the size of the
parameter space. The MCMC algorithm has a ``warm-up'' phase where it estimates
the size and shape of each dimension in the solution space.  Once this has been
completed, the models are sampled very quickly. In fact, there is little
difference between generating 1,000 or 10,000 models, although we find little
statistical difference after 1,000 models. For the mock lenses, the typical
``warm-up'' time was about 4s, and the modelling time was 20s using a parallel
shared-memory machine with 40 cores.

@@

\begin{enumerate}
\item one double and one extended double;
\item one quad and one extended quad;
\item two 2-source quads with varying redshift contrast.
\end{enumerate}
The `extended' configurations use multiple point sources at the same redshift
to simulate an extended source that will produces an arc-like image.
\figref{arrival surfaces} shows the lens configurations for the \mockBC\
galaxy. 
The configurations for the other galaxies are similar.  The labels Z1, Z2, Z3
within the names refer to the redshift of the sources. We have chosen Z1=1.72,
Z2=0.72, and Z3=0.51 so that the radial distribution of the images is roughly
equally spaced. For all mocks, we do not apply any external shear field.  Only
the central image of the Z1 source is used to avoid overconstraining the
models, otherwise all the central images would fall within the central pixel
and no solution exists that satisfies all locations simultaneously for one
pixel value.

@@

\figref{main results} and \figref{main results pixel-wise} show the results for
our full mock data ensemble. Each subplot corresponds to a different mock
galaxy, as marked. We show the fractional error of the mass distribution for
each of the test configurations with (red) and without (black) stellar mass. In
\figref{main results} we define the error
%
\begin{equation} \label{ferror R}
  f_R = \frac {\sum_i \left|M(i) - \tilde M(i)\right| } {\sum \tilde M(i)}
\end{equation}
%
based on the mass $M(i)$ of each pixel ring $i$ and the mass $\tilde M$ from the mock galaxy. 
In \figref{main results pixel-wise} the error is defined over all the pixels $\vec\theta$:
%
\begin{equation} \label{ferror theta}
f_\theta = \frac {\sum_{\vec\theta} \left|M(\vec\theta) - \tilde M(\vec\theta)\right| } {\sum_{\vec\theta} \tilde M(\vec\theta)}
\end{equation}
%
Since both error measurements consider the mass of each pixel, we are
implicitly weighting the recovered density by the varying size of the pixels.
The value $f_R$ emphasizes the error one would see from radial profiles, while
$f_\theta$ is useful as a measure of how well each individual pixel is recovered.
For both $f_R$ and $f_\theta$, we only consider mass up to one pixel length passed the
outermost image, since there is no longer any lensing information beyond that
point. This means we typically use 8 bins, linearly spaced, ignoring the
outermost 3 bins.  The spacing changes, however, at the border between the high
resolution region in the middle.
